### 2018-02-07 usenix18/ld.tex
more dirty tricks

To prove the correctness of \tool, we prove that  the observations in
source semantics and the distributed circuit semantics are identical
(\theoremref{correctness}).
We combine this correctness theorem and the security of the \mpc
back-end to prove security of the protocols generated by \tool
(\theoremref{security}).
%For the security of our compiler, we rely on the correctness guarantee and  reduce the security to the security of the underlying cryptographic protocol used to compute the generated circuit (see \theoremref{security}).
We present only selected parts of our formalization. Full definitions
and proofs can be found in~\cite{anonymized}.

@@

\end{array}
  \]
\caption{Source semantics (selected rules)}
\label{fig:srcsem}
\end{figure}

@@

  \end{array}
  \]
\caption{Source compilation (selected rules)}
\label{fig:compile}
\end{figure}

@@

\end{array}
  \]
\caption{Evaluation of Intermediate Language to Circuit (selected rules)}
\label{fig:eval-inter-circ}
\end{figure}

@@

    \inferrule*[lab={\footnotesize{C-Out}}]
               {
                 \widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \gate \Downarrow b_{1}, b_{2}\\\\
                 c = \mathcal{D}_{m}(b_{1}, b_{2})
               }
               {
                 \widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \kw{out}\:\gate \Downarrow \widehat{\rho}_{1}, \widehat{\rho}_{2}; c
               }
\end{array}
  \]
\caption{Circuit semantics in a distributed runtime (selected rules)}
\label{fig:cktsem}
\end{figure}

>>>>

To prove the correctness of \tool, we prove that  the observations in
source semantics and the distributed circuit semantics are identical
(\theoremref{correctness}).
We combine this correctness theorem and the security of the \mpc
back-end to prove security of the protocols generated by \tool
(\theoremref{security}).
%For the security of our compiler, we rely on the correctness guarantee and  reduce the security to the security of the underlying cryptographic protocol used to compute the generated circuit (see \theoremref{security}).
We present only selected parts of our formalization. Full definitions
and proofs can be found in the Appendix.

@@

\end{array}
  \]
\caption{Source semantics}
\label{fig:srcsem}
\end{figure}

@@

  \end{array}
  \]
\caption{Source compilation}
\label{fig:compile}
\end{figure}

@@

\end{array}
  \]
\caption{Evaluation of Intermediate Language to Circuit}
\label{fig:eval-inter-circ}
\end{figure}

@@

    \inferrule*[lab={\footnotesize{C-Out}}]
               {
                 \widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \gate \Downarrow b_{1}, b_{2}\\\\
                 c = \mathcal{D}_{m}(b_{1}, b_{2})
               }
               {
                 \widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \kw{out}\:\gate \Downarrow \widehat{\rho}_{1}, \widehat{\rho}_{2}; c
               }
\end{array}
  \]
\caption{Circuit semantics in a distributed runtime}
\label{fig:cktsem}
\end{figure}

### 2018-02-07 usenix18/pipe.tex
more dirty tricks

\paragraph{Implementing code partitioning.}
We use partitioning for programs that require large
circuits. Specifically, the programmer decomposes the program
$\prog$ into a sequence of small programs
$\prog_1\seq\dots\seq\prog_k$ manually. And then, \tool generates
sequence of programs $\progn_1,\dots\progn_k$ automatically. We then
compile and execute the $k$ programs
$\progn_1,\progn_2,\ldots,\progn_k$ sequentially, freeing up memory
usage after execution of each $\progn_i$.
Automating the manual decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program and we leave
the construction of such an analysis as future work. \nc{I changed the heading.}

>>>>

\paragraph{Implementing code partitioning.}
We use partitioning for programs that require large
circuits. Specifically, the programmer decomposes the program
$\prog$ into a sequence of small programs
$\prog_1\seq\dots\seq\prog_k$ manually. And then, \tool generates
sequence of programs $\progn_1,\dots\progn_k$ automatically. We then
compile and execute the $k$ programs
$\progn_1,\progn_2,\ldots,\progn_k$ sequentially, freeing up memory
usage after execution of each $\progn_i$.
Automating the manual decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program and we leave
the construction of such an analysis as future work.% \nc{I changed the heading.}
